### 2022-02-08 README.Rmd
update url redirects

An extensive and rapidly growing collection of richly annotated phylogenetics data is now available in the NeXML format. NeXML relies on state-of-the-art data exchange technology to provide a format that can be both validated and extended, providing a data quality assurance and adaptability to the future that is lacking in other formats. See [Vos et al 2012](http://doi.org/10.1093/sysbio/sys025 "NeXML: Rich, Extensible, and Verifiable Representation of Comparative Data and Metadata.") for further details on the NeXML format.

@@

> Boettiger C, Chamberlain S, Vos R and Lapp H (2016). “RNeXML: A Package for
> Reading and Writing Richly Annotated Phylogenetic, Character, and Trait Data
> in R.” _Methods in Ecology and Evolution_, **7**, pp. 352-357.
> [doi:10.1111/2041-210X.12469](http://doi.org/10.1111/2041-210X.12469)

Although the published version of the article is pay-walled, the source of the manuscript, and a much better rendered PDF, are included in this package (in the `manuscripts` folder). You can also find it [freely available on arXiv](http://arxiv.org/abs/1506.02722).

@@

[![ropensci footer](http://ropensci.org/public_images/github_footer.png)](http://ropensci.org)

>>>>

An extensive and rapidly growing collection of richly annotated phylogenetics data is now available in the NeXML format. NeXML relies on state-of-the-art data exchange technology to provide a format that can be both validated and extended, providing a data quality assurance and adaptability to the future that is lacking in other formats. See [Vos et al 2012](https://doi.org/10.1093/sysbio/sys025 "NeXML: Rich, Extensible, and Verifiable Representation of Comparative Data and Metadata.") for further details on the NeXML format.

@@

> Boettiger C, Chamberlain S, Vos R and Lapp H (2016). “RNeXML: A Package for
> Reading and Writing Richly Annotated Phylogenetic, Character, and Trait Data
> in R.” _Methods in Ecology and Evolution_, **7**, pp. 352-357.
> [doi:10.1111/2041-210X.12469](https://doi.org/10.1111/2041-210X.12469)

Although the published version of the article is pay-walled, the source of the manuscript, and a much better rendered PDF, are included in this package (in the `manuscripts` folder). You can also find it [freely available on arXiv](https://arxiv.org/abs/1506.02722).

@@

[![ropensci footer](https://ropensci.org//public_images/github_footer.png)](https://ropensci.org/)
